The Impact of Cloud Computing for Education and Business in $10$ Years

### 2013-05-06 essay/tex/essay.tex
final version

\section{Introduction}
In recent years, cloud computing has provided us with a lot of benefits in many area. Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource. For example, Amazon EC2\cite{garfinkel2007evaluation} is one of the most popular cloud computing platform for many companies and individuals. The various types of virtual instances at different price strategies provide very flexible choices for the users. I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $\$100$. With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $\$100$ for three years. Besides individual users like me, many companies either big ones like Netflix or startups like Pinterest choose Amazon AWS as their dedicated IT infrastructure to reduce the cost of maintaining a complete IT infrastructure by themselves.

@@

Furthermore, some challenges in the mobile computing are still unresolved. For example, the mobile network latency and battery issues which are critical to the usage fluency of mobile applications. To cope with the issues, some researchers propose the concept of \emph{Cloudlets}~\cite{satyanarayanan2009case} which bridges the mobile devices and the clouds through a middle station. To deal with the battery issues, some researchers proposes the \emph{offloading}~\cite{kumar2010cloud} techniques to transfer the computation from the mobile devices to the cloud. To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices. Therefore, we could see the cloud computing is not only a backend supporter but a key to solve problems in mobile computing as well.

\section{Education and Cloud Computing}
At the current stage, cloud computing seems to have little interactions with the education field, especially the primary and secondary educations. Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school systems will use a cloud email services from Google or Microsoft. My wife was once a substitute teacher in Webb school at Knoxville and Knox county schools. She tells me there is a big difference of the education philosophy and approach between Webb school and Knox county school. For Webb school, teaching has been digitalized. The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for readings, interactions and homeworks. There is no physical textbooks really necessary in my wife's teaching at Webb school. In addition to the course material, Webb school has a strong IT team to support the teachers and students. At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefit their teaching. For example, the students usually finish their homework on iPad and submit the assignment through an app. The teacher can grade it and analyze the performance of the student from its history very easily.

>>>>

\section{Introduction}
In recent years, cloud computing has provided us a lot of benefits in many area. Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource. For example, Amazon EC2\cite{garfinkel2007evaluation} is one of the most popular cloud computing platform for many companies and individuals. The various types of virtual instances at different price strategies provide very flexible choices for the users. I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $\$100$. With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $\$100$ for three years. Besides individual users like me, many companies either big ones like Netflix or startups like Pinterest choose Amazon AWS as their dedicated IT infrastructure to reduce the cost of maintaining a complete IT infrastructure by themselves.

@@

Furthermore, some challenges in the mobile computing are still unresolved. For example, the mobile network latency and battery issues which are critical to the usage fluency of mobile applications. To cope with the issues, some researchers propose the concept of \emph{Cloudlets}~\cite{satyanarayanan2009case} which bridges the mobile devices and the clouds through a middle station. To deal with the battery issues, some researchers proposes the \emph{offloading}~\cite{kumar2010cloud} techniques to transfer the computation from the mobile devices to the cloud. To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices. Therefore, we could see the cloud computing is not only a backend supporter but a key to solve problems in mobile computing research as well.

\section{Education and Cloud Computing}
At the current stage, cloud computing seems to have few interactions with the education field, especially the primary and secondary educations. Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school systems will use a cloud email services from Google or Microsoft. My wife was once a substitute teacher in Webb school at Knoxville and Knox county schools. She tells me there is a big difference of the education philosophy and approach between Webb school and Knox county school. For Webb school, teaching has been digitalized. The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for readings, interactions and homeworks. There is no physical textbooks really necessary in my wife's teaching at Webb school. In addition to the course material, Webb school has a strong IT team to support the teachers and students. At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefit their teaching. For example, the students usually finish their homework on iPad and submit the assignment through an app. The teacher can grade it and analyze the performance of the student from its history very easily.
